A state of the art end-to-end speech recognition algorithm with a homogenous structure.

### 2019-05-04 none_feedback_sequence_classifier/doc/main.tex
Updates the paper

\usepackage{nips_2017}

@@

\newcommand{\chanwcom}{{C. Kim}}
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\renewcommand{\floatpagefraction}{0.85}

@@

\begin{abstract}
TODO(chanw.com) Revise the abstract.
This paper proposes a new end-to-end speech recognition system referred to
as Recurrent neural network Sequence Classification (RSC). Recently, end-to-end speech
recognition systems have been gaining more attention from researchers and
several different structures have been proposed. Typical examples  
include Connectionist Temporal Classification (CTC), Recurrent Neural Network
  Transducer (RNN-T), and Sequence-to-Sequence Modeling using the attention
mechanism. The CTC-based approaches are using the CTC loss assuming the
conditional independence property. Although the structure of CTC is simpler
than other end-to-end systems, the performance is worse due to this conditional
independence assumption. RNN-T and attention-based approaches have distinct
components such as the prediction network  and encoder in RNN-T, and
the encoder, the decoder, and the attention layer in the attention-based model.
Compared to these models, SHC has a homogeneous structure from the bottom to 
the top layer. LSTM and max-pooling layer are repeated followed by the top
softmax layer. The embedded softmax output is fed back as input of each RNN
layer. The training starts with flat initialization and alignment is made
after every epoch. The loss is the Cross Entropy (CE) loss using this 
alignment result. In our experimental results, SHC algorithm has shown 
better performance than more complicated attention-based end-to-end speech
recognition system. Another major advantage is training is significantly
faster.
\end{abstract}

\section{Introduction}

Recently, deep neural network has significantly improved the performance
of speech recognition systems \cite{}.

\section{Review of end-to-end speech recognition systems}

\begin{figure}
    \centering
    \resizebox{40mm}{!}{%
         \input{../figures/ctc.tex}} %
    \caption {
      The entire structure of the sequence homogeneously-structured classifier
      (SHC).
      \label{fig:ctc_diagram}
    }
    %\end{center}
\end{figure}
Recently, there have been growing interests in end-to-end speech
recognition systems.  [CITE] Fig. \ref{fig:ctc_diagram} shows the
entire structure of the Connectionist Temporal Classification (CTC) 
and the attention-based end-to-end speech recognition system.

\section{Sequence Homogeneously-Structured Classifier}
Figure \ref{} shows the entire structure of the SHC. Speech-recognition
task can be also considered as a

\subsection{The structure of the Sequence Homogeneously-Structured Classifier}

Fig. \label{fig:entire_diagram} shows the block diagram for
enhancing the noisy feature.

\begin{figure}
    \centering
    \resizebox{50mm}{!}{%
         \input{../figures/shc_diagram.tex}} %
    \caption {
      The entire structure of the sequence homogeneously-structured classifier
      (SHC).
      \label{fig:shc_diagram}
    }
    %\end{center}
\end{figure}

Fig. \ref{fig:shc_diagram} shows the structure of the SHC algorithm. The
structure is very simple and somewhat similar to that of CTC shown in TODO

\subsection{Training of the Sequence Homogeneously-Structured Classifier}
In this section, we describe how to train SHC. The procedure is summarized
in the following table.

@@

\subsection{Feature extraction}

Even though the log-mel coefficients have been widely used
as features for speech recognition \cite{sbdavisandpm1980},
the log non-linearity has a disadvantage in that the value
diverges to negative infinity as the mel filterbank coefficient
approaches zero \cite{C_Kim_IEEETran_2016_1}.
Thus, we use the power-law nonlinearity
rather than the log-nonlinearity:
\begin{align}
  q[m, l] =  (p[m, l])^{\frac{1}{15}}
  \label{eq:power_law_nonlineartiy}
\end{align}
We use the power coefficient of $\frac{1}{15}$ as in
\cite{C_Kim_IEEETran_2016_1, C_Kim_ICASSP_2012_1}.

In this section, we discuss how to predict the clean feature and the
error ratio from the corrupt feature. Let us denote the clean target feature,
the corrupt feature by $\boldsymbol{x}, \boldsymbol{y}$ respectively.

Using the room simulation system described in \cite{C_Kim_INTERSPEECH_2017_1},
we create a pair of clean and
corrupt utterances. Log-mel [XX] features are calculated from these original clean
and corrupt utterances. Let us denote the clean feature by $\boldsymbol{t}_i$ and
the simulated corrupt feature by $\boldsymbol{x}_i$, respectively where $i$ is the
utterance index. The training set is represented by the following set:
\begin{align}
  \mathcal{T} = \{<\boldsymbol{x}_i, \boldsymbol{t}_i>| 0 \le i \le N - 1\}
\end{align}
where $N$ is the number of training examples.

In the ECE algorithm, we first estimate the true target $\boldsymbol{t}_i$. The
estimation error is defined by the following equation:
\begin{align}
  \boldsymbol{e}_i =  \boldsymbol{t}_i - \boldsymbol{x}_i, \quad 0 \le i \le N - 1
\end{align}

The norm of the error vector $\boldsymbol{e}_i$ would be generally large when
the norm of the estimated clean feature is large.

Thus, instead of trying to estimate the error itself, the neural network tries to
estimate the error ratio given as follows:

\begin{align}
  r_i = {}{}
\end{align}

\section{Generation of simulated clean and noisy data sets}
\label{gen_inst}

To train neural networks described in section \ref{sec:estimation}, we
need a training set consisting of pairs of clean speech and noisy speech.
Unfortunately, it is not easy to have such a training set from real speech
utterances. Thus, we use the simulation system described in
\cite{C_Kim_INTERSPEECH_2017_1} to synthetically generate noisy speech
utterances from the clean speech utterances.

In our application, for clean training set, we used Wall Street Journal (WSJ)
si-284. For noise set, we used the Resource Management 1 (RM1)
\cite{price_p_ldc_1993} 50 \% of time 
and DEMAND noise [TODO(chanwcom) Adds reference] for the remaining 50 \% of time.

TODO(chanwcom) Cite DEMAND noise set.

%
%
%
%\begin{figure*}
%  \centering
%    \begin{subfigure}[\label{fig:randomly_selected_grid_coordinates}]{0.5\textwidth} {
%        \includegraphics[width=\textwidth]{target_estimation}}
%    \caption{Grid from random-sampling}
%    \end{subfigure}
%   % \begin{subfigure}[\label{fig:intersection_point}]{0.5\textwidth} {
%   %   \includegraphics[width=\textwidth]{intersection_point}}
%   % \caption{Calculation of grid coordinates}
%   % \end{subfigure}
%  \caption {Random Grid Sampling}
%\end{figure*}
%
%
%
\section{Estimation of the optimal weight in the EFW algorithm}
In this section, we describe the procedure of feature weighting approach.
Suppose that the feature before enhancement is represented by $\vec{x}$.
Let us represent the inference neural network to estimate the target by
$\mathcal{T}$.

\begin{align}
  \mathcal{X} = \{  \}
\end{align}

Instead of directly using the enhanced feature $\widehat{\vec{y}}$, we consider
the following interpolated feature $\bm{z}$ from the original corrupt
input $\bm{x}$ and .
\begin{align}
  \vec{z} = \vec{w} \odot \widehat{\vec{y}} \ + (1 - \vec{w}) \odot \vec{x} 
    \label{eq:vec_z}
\end{align}
where $\odot$ denotes the Hadamard product (entry-wise product).

Let us denote the estimated variance vector by $\hat{\vec{v}}$:
\begin{align}
  \hat{\vec{v}} & = \text{Var}[\widehat{\vec{y}}] \nonumber \\
                & = E[(y - y)^2 | \vec{x}[0], \vec{x}[1], ... \vec{x}[T]]
     \label{eq:vec_v}
\end{align}

In our discussion, let us assume that the expectation of $\hat{\vec{y}}$ is the
same as the true target $\vec{y}$.
\begin{align}
  E[\widehat{\vec{y}}] = \vec{y}  \label{eq:expectation_of_y}
\end{align}

Now, let us obtain the expected value of $\vec{z}$ from
\eqref{eq:vec_z} and \eqref{eq:expectation_of_y}
\begin{align}
  E[\vec{z}] = (1 - \vec{w}) \odot (\vec{x} - \vec{y})
\end{align}
Thus, the bias of $\vec{z}$ is given by:
\begin{align}
  Bias_{\vec{z}} & = E[\vec{z}] - t \nonumber \\
                 & = \vec{w} \odot (\widehat{\vec{y}} - \vec{y})
\end{align}

From \eqref{eq:vec_z} and \eqref{eq:vec_v}, the variance of $\vec{z}$ is given by:
\begin{align}
  Var_{\vec{z}} = \vec{v} \odot w \odot w.
\end{align}
The mean squared error of the $i$-th element of the $\vec{z}$ is given by:
\begin{align}
  MSE_{\vec{z_i}} & = Bias_{\vec{z_i}}^2 + Var_{\vec{z_i}} \nonumber \\
                 & =  \left[(\vec{x}_i - \vec{y}_i) ^ 2
                    + \vec{v}_i^2 \right] \vec{w}_i^{2}
                    - 2 (\vec{x}_i - \vec{y}_i)^{2}  \vec{w}_i
                    + (\vec{x}_i - \vec{y}_i)^{2}
 \label{eq:mse_z_i}
\end{align}
Since the above equation \eqref{eq:mse_z_i} is a quadratic equation with
respect to $\vec{w}_i$, we may find that the minimum value of $MSE_{\vec{z_i}}$
is obtained when $\vec{w}_i$ has the following value:
\begin{align}
  \vec{w}_i = \frac{(\vec{x}_i - \vec{y}_i)^2}{(\vec{x}_i - \vec{y}_i)^2 + \vec{v}_i}
\end{align}

Thus, the final form of the estimated vector $\widehat{\vec{z}}$ becomes:
\begin{align}
  \widehat{\vec{z}} = \widehat{\vec{w}} \odot \widehat{\vec{y}}
    \ + (1 - \widehat{\vec{w}}) \odot \vec{x}
\end{align}
where
\begin{align}
  \widehat{\vec{w}} = {(\vec{x} - \vec{y})^{\odot 2}}
    \left[(\vec{x} - \vec{y})^{\odot 2}+ \vec{v}\right]^{\odot -1}.
\end{align}

Sequence enhancement

The feature enhancement is to map a sequence of corrupt features $\mathbf{X}$.
\begin{subequations}
  \begin{align}
    \mathbf{X} = \left(\vec{x}[0], \vec{x}[1], \cdots, \vec{x}[M-1] \right)  \\
    \mathbf{Y} = \left(\vec{y}[0], \vec{y}[1], \cdots, \vec{y}[M-1] \right) 
  \end{align}
\end{subequations}

>>>>

\usepackage{neurips_2019}

@@

\newcommand{\chanwcom}{Chanwoo Kim}
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\renewcommand{\floatpagefraction}{0.85}

@@

\begin{abstract}
TODO(chanw.com) Revise the abstract.
This paper proposes a new end-to-end speech recognition system referred to
as Recurrent neural network Sequence Classification (RSC). Recently, end-to-end speech
recognition systems have been gaining more attention from researchers and
several different structures have been proposed. Typical examples  
include Connectionist Temporal Classification (CTC), Recurrent Neural Network
  Transducer (RNN-T), and Sequence-to-Sequence Modeling using the attention
mechanism. The CTC-based approaches are using the CTC loss assuming the
conditional independence property. Although the structure of CTC is simpler
than other end-to-end systems, the performance is worse due to this conditional
independence assumption. RNN-T and attention-based approaches have distinct
components such as the prediction network  and encoder in RNN-T, and
the encoder, the decoder, and the attention layer in the attention-based model.
Compared to these models, FSC has a homogeneous structure from the bottom to 
the top layer. LSTM and max-pooling layer are repeated followed by the top
softmax layer. The embedded softmax output is fed back as input of each RNN
layer. The training starts with flat initialization and alignment is made
after every epoch. The loss is the Cross Entropy (CE) loss using this 
alignment result. In our experimental results, FSC algorithm has shown 
better performance than more complicated attention-based end-to-end speech
recognition system. Another major advantage is training is significantly
faster.
\end{abstract}

\section{Introduction}
Recently, there has been tremendous improvements in speech recognition
systems fueled by advances in deep neural networks
\cite{
  Yu2013FeatureLearningDNN, 
  g_hinton_ieee_signal_processing_mag_2012,
  Seltzer2013DNNAurora4, 
  t_sainath_taslp_2017_00,
  t_sainath_book_chapter_2017_00,
  v_vanhoucke_nips_workshop_2011_00}.

TODO(chanw.com) Talk about the AI speakers.

TODO(chanw.com) Talk about the advancements of the end-to-end systems.

Recently, it has been frequently observed that if 
sequence-to-sequence end-to-end ASR systems are trained on sufficiently 
large amounts of acoustic training data, they can outperform
conventional HMM-DNN/RNN hybrid systems \cite{c_chiu_icassp_2018_00, 
c_kim_interspeech_2019_00}.

Recently, we observed that training with large-scale noisy data generated
by a \textit{Room Simulator} \cite{C_Kim_INTERSPEECH_2017_1}
improves speech recognition accuracy dramatically.
This system has been successfully employed
for training acoustic models for Google Home or Google voice
search \cite{C_Kim_INTERSPEECH_2017_1}.

\section{Review on sequence-to-sequence speech recognition algorithms}

In this section, we review well-known {\it sequence-to-sequence} algorithms
used in speech recognition.
\cite{
j_chorowski_nips_2015_00, 
a_graves_corr_2012_00, 
y_he_icassp_2019_00,
r_prabhavalkar_interspeech_2017_00}. 
A sequence-to-sequence
model maps a sequence of input acoustic features into a sequence 
of graphemes or words \cite{r_prabhavalkar_interspeech_2017_00}. 
We denote a sequence of input acoustic feature vectors by 
$\mathcal{X}_{0}^{M-1}$ and a sequence of target labels by 
$\mathcal{Y}_{0}^{L-1}$:
\begin{subequations}
  \begin{align}
    \mathcal{X}_{0}^{}  =  
      \left\{\vec{x}[0], \, \vec{x}[1], 
        \, \cdots, \, \vec{x}[M-1] \right\},  \\
    \mathcal{Y}_{0}^{}  =  
      \left\{y_0, \, y_1, \,  \cdots, \, y_{L-1} \right\},
  \end{align}
\end{subequations}
where $M$ is the number of frames in the input feature sequence and
$L$ is the number of labels in the output target sequence. In Fig. 
\ref{fig:ctc_diagram} $\sim$ \ref{fig:attention_diagram}, we show
block diagrams of CTC \cite{a_graves_icml_2006_00}, 
RNN-T \cite{a_graves_corr_2012_00, a_graves_icassp_2013_00}, and 
the attention-based model 
\cite{
j_chorowski_nips_2015_00,
w_chan_icassp_2016_00} respectively. CTC in Fig. \ref{fig:ctc_diagram} 
and RNN-T in Fig. \ref{fig:rnn_t_diagram} are {\it frame-synchronous}, 
which means that the ASR system generates the output target for each 
input frame.

\subsection{Connectionist Temporal Classification}

Fig. \ref{fig:ctc_diagram} shows the entire structure of the 
Connectionist Temporal Classification (CTC) 
\cite{a_graves_icml_2006_00}. In CTC, we use the following CTC loss
\cite{a_graves_icml_2006_00, y_he_icassp_2019_00}:
\begin{align}
  P\left(\mathcal{Y}_{0}^{L-1} | \mathcal{X}_{0}^{M-1}\right) = 
    \sum_{\mathcal{Z}_{0}^{M-1} \in 
      \mathcal{A}_{CTC} 
        \left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1} \right)}
          \Pi_{m=0}^{M-1}
            P\left(\vec{z}[m] | \mathcal{X}_{0}^{M-1} \right),
\end{align}
where $\mathcal{A}_{CTC} \left(\mathcal{X}_{0}^{M-1}, 
\mathcal{Y}_{0}^{L-1} \right)$ correspond to frame-level alignments
of length $M$ such that removing blanks and repeated symbols from 
$\mathcal{Z}_{0}^{M-1}$ yields $\mathcal{Y}_{0}^{L-1}$.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.35\textwidth}
    \centering
    \resizebox{23mm}{!}{
      \input{../figures/ctc_diagram.tex}
    } 
    \caption {
      Connectionist Temporal Classification (CTC) Model.
      \label{fig:ctc_diagram}
    }
  \end{subfigure}
  \begin{subfigure}[b]{0.60\textwidth}
    \centering
    \resizebox{78mm}{!}{
      \input{../figures/rnn_t_diagram.tex}
    }
    \caption {
      RNN-T Model.
      \label{fig:rnn_t_diagram}
    }
  \end{subfigure}

  \begin{subfigure}[b]{0.55\textwidth}
    \centering
    \resizebox{53mm}{!}{
      \input{../figures/attention_diagram.tex}
    }
    \caption {
      Attention-based Model.
      \label{fig:attention_diagram}
    }
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \resizebox{26mm}{!}{
      \input{../figures/fsc_diagram.tex}
    }
    \caption {
      Feedback Sequence Classifier (FSC) Model.
      \label{fig:fsc_diagram}
    }
  \end{subfigure}
  \caption{
    Comparison of block diagrams of different sequence-to-sequence speech
    recognition approaches.
    The proposed Feedback Sequence Classifier (FSC) is shown in 
    Fig. \ref{fig:fsc_diagram}.
  }

\end{figure}

\section{Feedback Sequence Classifier}
\label{sec:feedback_sequence_classifier}

\subsection{Neural Network Structure}
Fig. \ref{fig:fsc_diagram} shows the entire structure of the FSC. 
As shown in this figure, LSTM layers and max-pool layers
are interleaved from the bottom layer up to the third max-pool layer.

In Fig. \ref{fig:fsc_diagram}, speech features $\vec{x}[m]$ are sampled 
at every 10 {\it ms}, which is the usual speech feature frame rate  
in speech recognition
\cite{x_huang_prentice_hall_2001_00, c_kim_taslp_2016_00},
Using three two-to-one max-pool layers, $\vec{z}[p]$ has a frame period 
of 80 {\it ms}.  
The relationship between the temporal index $p$ in $\vec{z}[p]$ and 
$m$ in $\vec{x}[m]$ is given by: 
\begin{align}
  p = \lceil m / 8 \rceil \label{eq:def_p}
\end{align}

The reason for using the one dimensional max-pool layer
is to make the neural network output have a similar rate to the 
that of each {\it phone} in utterances. Note that a {\it phone} 
is any distinct speech sound serving as a phonetic unit.

It has been observed that the average phone duration is between 50 {\it ms}
\textasciitilde 100 {\it ms} \cite{x_wang_icslp_1996_00, z_bartosz_ltc_2009_00}.

\subsection{Training of the Feedback Sequence Classifier}
In this section, we describe how to train FSC. The first step is making an
alignment using the N-best alignment. The second step is updating the
neural network parameters using the Cross Entropy (CE) criterion.

\subsection{Training procedure}

The first step is finding the optimal frame-synchronous sequence
$\mathcal{Z}$

\begin{algorithmic}
  \State {$\mathcal{Z} = A(\mathcal{X} | \Theta)$}
  \State {Updates the model.}
\end{algorithmic}

@@

\section{Experimental Results}
\label{sec:experimental_results}
